Grid Test

### 2022-10-07 graphs_newt_snakes/grid_test.Rmd
looking at grids and started the cost markdown. I am also tring to put a map into my slim sim

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=GA1_dif_grid
thefolder=${thepath}${foldername}/*

@@

GA1_lit_grid_file<- read.csv("~/Desktop/GA1_dif_grid/all_lit.txt" , header = TRUE)
GA1_lit_grid_file$group_rep <- paste0(GA1_lit_grid_file$snake_mu_rate, "_", GA1_lit_grid_file$snake_mu_effect_sd,"_",GA1_lit_grid_file$newt_mu_rate, "_", GA1_lit_grid_file$newt_mu_effect_sd, "_", GA1_lit_grid_file$rep)
GA1_lit_grid_file$group <- paste0(GA1_lit_grid_file$snake_mu_rate, "_", GA1_lit_grid_file$snake_mu_effect_sd,"_",GA1_lit_grid_file$newt_mu_rate, "_", GA1_lit_grid_file$newt_mu_effect_sd)
GA1_lit_grid_file$sim=LETTERS[factor(GA1_lit_grid_file$group)]

GA1_cor_grid_2_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_2.txt" , header = TRUE)
GA1_cor_grid_2_file$group_rep <- paste0(GA1_cor_grid_2_file$snake_mu_rate, "_", GA1_cor_grid_2_file$snake_mu_effect_sd,"_",GA1_cor_grid_2_file$newt_mu_rate, "_", GA1_cor_grid_2_file$newt_mu_effect_sd, "_", GA1_cor_grid_2_file$rep)
GA1_cor_grid_2_file$group <- paste0(GA1_cor_grid_2_file$snake_mu_rate, "_", GA1_cor_grid_2_file$snake_mu_effect_sd,"_",GA1_cor_grid_2_file$newt_mu_rate, "_", GA1_cor_grid_2_file$newt_mu_effect_sd)
GA1_cor_grid_2_file$sim=LETTERS[factor(GA1_cor_grid_2_file$group)]
GA1_cor_grid_2_file$grid_num = 2

GA1_cor_grid_3_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_3.txt" , header = TRUE)
GA1_cor_grid_3_file$group_rep <- paste0(GA1_cor_grid_3_file$snake_mu_rate, "_", GA1_cor_grid_3_file$snake_mu_effect_sd,"_",GA1_cor_grid_3_file$newt_mu_rate, "_", GA1_cor_grid_3_file$newt_mu_effect_sd, "_", GA1_cor_grid_3_file$rep)
GA1_cor_grid_3_file$group <- paste0(GA1_cor_grid_3_file$snake_mu_rate, "_", GA1_cor_grid_3_file$snake_mu_effect_sd,"_",GA1_cor_grid_3_file$newt_mu_rate, "_", GA1_cor_grid_3_file$newt_mu_effect_sd)
GA1_cor_grid_3_file$sim=LETTERS[factor(GA1_cor_grid_3_file$group)]
GA1_cor_grid_3_file$grid_num = 3

GA1_cor_grid_4_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_4.txt" , header = TRUE)
GA1_cor_grid_4_file$group_rep <- paste0(GA1_cor_grid_4_file$snake_mu_rate, "_", GA1_cor_grid_4_file$snake_mu_effect_sd,"_",GA1_cor_grid_4_file$newt_mu_rate, "_", GA1_cor_grid_4_file$newt_mu_effect_sd, "_", GA1_cor_grid_4_file$rep)
GA1_cor_grid_4_file$group <- paste0(GA1_cor_grid_4_file$snake_mu_rate, "_", GA1_cor_grid_4_file$snake_mu_effect_sd,"_",GA1_cor_grid_4_file$newt_mu_rate, "_", GA1_cor_grid_4_file$newt_mu_effect_sd)
GA1_cor_grid_4_file$sim=LETTERS[factor(GA1_cor_grid_4_file$group)]
GA1_cor_grid_4_file$grid_num = 4

GA1_cor_grid_5_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_5.txt" , header = TRUE)
GA1_cor_grid_5_file$group_rep <- paste0(GA1_cor_grid_5_file$snake_mu_rate, "_", GA1_cor_grid_5_file$snake_mu_effect_sd,"_",GA1_cor_grid_5_file$newt_mu_rate, "_", GA1_cor_grid_5_file$newt_mu_effect_sd, "_", GA1_cor_grid_5_file$rep)
GA1_cor_grid_5_file$group <- paste0(GA1_cor_grid_5_file$snake_mu_rate, "_", GA1_cor_grid_5_file$snake_mu_effect_sd,"_",GA1_cor_grid_5_file$newt_mu_rate, "_", GA1_cor_grid_5_file$newt_mu_effect_sd)
GA1_cor_grid_5_file$sim=LETTERS[factor(GA1_cor_grid_5_file$group)]
GA1_cor_grid_5_file$grid_num = 5

GA1_cor_grid_6_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_6.txt" , header = TRUE)
GA1_cor_grid_6_file$group_rep <- paste0(GA1_cor_grid_6_file$snake_mu_rate, "_", GA1_cor_grid_6_file$snake_mu_effect_sd,"_",GA1_cor_grid_6_file$newt_mu_rate, "_", GA1_cor_grid_6_file$newt_mu_effect_sd, "_", GA1_cor_grid_6_file$rep)
GA1_cor_grid_6_file$group <- paste0(GA1_cor_grid_6_file$snake_mu_rate, "_", GA1_cor_grid_6_file$snake_mu_effect_sd,"_",GA1_cor_grid_6_file$newt_mu_rate, "_", GA1_cor_grid_6_file$newt_mu_effect_sd)
GA1_cor_grid_6_file$sim=LETTERS[factor(GA1_cor_grid_6_file$group)]
GA1_cor_grid_6_file$grid_num = 6

GA1_cor_grid_7_file<- read.csv("~/Desktop/GA1_dif_grid/all_cor_7.txt" , header = TRUE)
GA1_cor_grid_7_file$group_rep <- paste0(GA1_cor_grid_7_file$snake_mu_rate, "_", GA1_cor_grid_7_file$snake_mu_effect_sd,"_",GA1_cor_grid_7_file$newt_mu_rate, "_", GA1_cor_grid_7_file$newt_mu_effect_sd, "_", GA1_cor_grid_7_file$rep)
GA1_cor_grid_7_file$group <- paste0(GA1_cor_grid_7_file$snake_mu_rate, "_", GA1_cor_grid_7_file$snake_mu_effect_sd,"_",GA1_cor_grid_7_file$newt_mu_rate, "_", GA1_cor_grid_7_file$newt_mu_effect_sd)
GA1_cor_grid_7_file$sim=LETTERS[factor(GA1_cor_grid_7_file$group)]
GA1_cor_grid_7_file$grid_num = 7

# GA1_grid_grid_2_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_2.txt" , header = TRUE)
# GA1_grid_grid_2_file$group_rep <- paste0(GA1_grid_grid_2_file$snake_mu_rate, "_", GA1_grid_grid_2_file$snake_mu_effect_sd,"_",GA1_grid_grid_2_file$newt_mu_rate, "_", GA1_grid_grid_2_file$newt_mu_effect_sd, "_", GA1_grid_grid_2_file$rep)
# GA1_grid_grid_2_file$group <- paste0(GA1_grid_grid_2_file$snake_mu_rate, "_", GA1_grid_grid_2_file$snake_mu_effect_sd,"_",GA1_grid_grid_2_file$newt_mu_rate, "_", GA1_grid_grid_2_file$newt_mu_effect_sd)
# GA1_grid_grid_2_file$sim=LETTERS[factor(GA1_grid_grid_2_file$group)]
# GA1_grid_grid_2_file$grid_num = 2
# 
# 
# GA1_grid_grid_3_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_3.txt" , header = TRUE)
# GA1_grid_grid_3_file$group_rep <- paste0(GA1_grid_grid_3_file$snake_mu_rate, "_", GA1_grid_grid_3_file$snake_mu_effect_sd,"_",GA1_grid_grid_3_file$newt_mu_rate, "_", GA1_grid_grid_3_file$newt_mu_effect_sd, "_", GA1_grid_grid_3_file$rep)
# GA1_grid_grid_3_file$group <- paste0(GA1_grid_grid_3_file$snake_mu_rate, "_", GA1_grid_grid_3_file$snake_mu_effect_sd,"_",GA1_grid_grid_3_file$newt_mu_rate, "_", GA1_grid_grid_3_file$newt_mu_effect_sd)
# GA1_grid_grid_3_file$sim=LETTERS[factor(GA1_grid_grid_3_file$group)]
# GA1_grid_grid_3_file$grid_num = 3
# 
# GA1_grid_grid_4_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_4.txt" , header = TRUE)
# GA1_grid_grid_4_file$group_rep <- paste0(GA1_grid_grid_4_file$snake_mu_rate, "_", GA1_grid_grid_4_file$snake_mu_effect_sd,"_",GA1_grid_grid_4_file$newt_mu_rate, "_", GA1_grid_grid_4_file$newt_mu_effect_sd, "_", GA1_grid_grid_4_file$rep)
# GA1_grid_grid_4_file$group <- paste0(GA1_grid_grid_4_file$snake_mu_rate, "_", GA1_grid_grid_4_file$snake_mu_effect_sd,"_",GA1_grid_grid_4_file$newt_mu_rate, "_", GA1_grid_grid_4_file$newt_mu_effect_sd)
# GA1_grid_grid_4_file$sim=LETTERS[factor(GA1_grid_grid_4_file$group)]
# GA1_grid_grid_4_file$grid_num = 4
# 
# GA1_grid_grid_5_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_5.txt" , header = TRUE)
# GA1_grid_grid_5_file$group_rep <- paste0(GA1_grid_grid_5_file$snake_mu_rate, "_", GA1_grid_grid_5_file$snake_mu_effect_sd,"_",GA1_grid_grid_5_file$newt_mu_rate, "_", GA1_grid_grid_5_file$newt_mu_effect_sd, "_", GA1_grid_grid_5_file$rep)
# GA1_grid_grid_5_file$group <- paste0(GA1_grid_grid_5_file$snake_mu_rate, "_", GA1_grid_grid_5_file$snake_mu_effect_sd,"_",GA1_grid_grid_5_file$newt_mu_rate, "_", GA1_grid_grid_5_file$newt_mu_effect_sd)
# GA1_grid_grid_5_file$sim=LETTERS[factor(GA1_grid_grid_5_file$group)]
# GA1_grid_grid_5_file$grid_num = 5
# 
# GA1_grid_grid_6_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_6.txt" , header = TRUE)
# GA1_grid_grid_6_file$group_rep <- paste0(GA1_grid_grid_6_file$snake_mu_rate, "_", GA1_grid_grid_6_file$snake_mu_effect_sd,"_",GA1_grid_grid_6_file$newt_mu_rate, "_", GA1_grid_grid_6_file$newt_mu_effect_sd, "_", GA1_grid_grid_6_file$rep)
# GA1_grid_grid_6_file$group <- paste0(GA1_grid_grid_6_file$snake_mu_rate, "_", GA1_grid_grid_6_file$snake_mu_effect_sd,"_",GA1_grid_grid_6_file$newt_mu_rate, "_", GA1_grid_grid_6_file$newt_mu_effect_sd)
# GA1_grid_grid_6_file$sim=LETTERS[factor(GA1_grid_grid_6_file$group)]
# GA1_grid_grid_6_file$grid_num = 6
# 
# GA1_grid_grid_7_file<- read.csv("~/Desktop/GA1_dif_grid/all_grid_7.txt" , header = TRUE)
# GA1_grid_grid_7_file$group_rep <- paste0(GA1_grid_grid_7_file$snake_mu_rate, "_", GA1_grid_grid_7_file$snake_mu_effect_sd,"_",GA1_grid_grid_7_file$newt_mu_rate, "_", GA1_grid_grid_7_file$newt_mu_effect_sd, "_", GA1_grid_grid_7_file$rep)
# GA1_grid_grid_7_file$group <- paste0(GA1_grid_grid_7_file$snake_mu_rate, "_", GA1_grid_grid_7_file$snake_mu_effect_sd,"_",GA1_grid_grid_7_file$newt_mu_rate, "_", GA1_grid_grid_7_file$newt_mu_effect_sd)
# GA1_grid_grid_7_file$sim=LETTERS[factor(GA1_grid_grid_7_file$group)]
# GA1_grid_grid_7_file$grid_num = 7

@@

# all_grid_grid = rbind(GA1_grid_grid_2_file, GA1_grid_grid_3_file, GA1_grid_grid_4_file,  GA1_grid_grid_5_file,  GA1_grid_grid_6_file,  GA1_grid_grid_7_file)
# 
# all_grid_grid$group_exp=paste0(all_grid_grid$group, "_", all_grid_grid$experiment)
# all_grid_grid$exp_group=paste0(all_grid_grid$experiment, "_", all_grid_grid$group)

@@

>>>>

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=GA1_dif_grids
thefolder=${thepath}${foldername}/*

@@

GA1_lit_grid_file<- read.csv("~/Desktop/GA1_dif_grids/all_lit.txt" , header = TRUE)
GA1_lit_grid_file$group_rep <- paste0(GA1_lit_grid_file$snake_mu_rate, "_", GA1_lit_grid_file$snake_mu_effect_sd,"_",GA1_lit_grid_file$newt_mu_rate, "_", GA1_lit_grid_file$newt_mu_effect_sd, "_", GA1_lit_grid_file$rep)
GA1_lit_grid_file$group <- paste0(GA1_lit_grid_file$snake_mu_rate, "_", GA1_lit_grid_file$snake_mu_effect_sd,"_",GA1_lit_grid_file$newt_mu_rate, "_", GA1_lit_grid_file$newt_mu_effect_sd)
GA1_lit_grid_file$sim=LETTERS[factor(GA1_lit_grid_file$group)]
GA1_lit_grid_file$dif=GA1_lit_grid_file$Snake_mean_Pheno-GA1_lit_grid_file$Newt_mean_Pheno

GA1_cor_grid_2_file<- read.csv("~/Desktop/GA1_dif_grids/all_cor_2.txt" , header = TRUE)
GA1_cor_grid_2_file$group_rep <- paste0(GA1_cor_grid_2_file$snake_mu_rate, "_", GA1_cor_grid_2_file$snake_mu_effect_sd,"_",GA1_cor_grid_2_file$newt_mu_rate, "_", GA1_cor_grid_2_file$newt_mu_effect_sd, "_", GA1_cor_grid_2_file$rep)
GA1_cor_grid_2_file$group <- paste0(GA1_cor_grid_2_file$snake_mu_rate, "_", GA1_cor_grid_2_file$snake_mu_effect_sd,"_",GA1_cor_grid_2_file$newt_mu_rate, "_", GA1_cor_grid_2_file$newt_mu_effect_sd)
GA1_cor_grid_2_file$sim=LETTERS[factor(GA1_cor_grid_2_file$group)]
GA1_cor_grid_2_file$grid_num = 2

GA1_cor_grid_3_file<- read.csv("~/Desktop/GA1_dif_grids/all_cor_3.txt" , header = TRUE)
GA1_cor_grid_3_file$group_rep <- paste0(GA1_cor_grid_3_file$snake_mu_rate, "_", GA1_cor_grid_3_file$snake_mu_effect_sd,"_",GA1_cor_grid_3_file$newt_mu_rate, "_", GA1_cor_grid_3_file$newt_mu_effect_sd, "_", GA1_cor_grid_3_file$rep)
GA1_cor_grid_3_file$group <- paste0(GA1_cor_grid_3_file$snake_mu_rate, "_", GA1_cor_grid_3_file$snake_mu_effect_sd,"_",GA1_cor_grid_3_file$newt_mu_rate, "_", GA1_cor_grid_3_file$newt_mu_effect_sd)
GA1_cor_grid_3_file$sim=LETTERS[factor(GA1_cor_grid_3_file$group)]
GA1_cor_grid_3_file$grid_num = 3

GA1_cor_grid_4_file<- read.csv("~/Desktop/GA1_dif_grids/all_cor_4.txt" , header = TRUE)
GA1_cor_grid_4_file$group_rep <- paste0(GA1_cor_grid_4_file$snake_mu_rate, "_", GA1_cor_grid_4_file$snake_mu_effect_sd,"_",GA1_cor_grid_4_file$newt_mu_rate, "_", GA1_cor_grid_4_file$newt_mu_effect_sd, "_", GA1_cor_grid_4_file$rep)
GA1_cor_grid_4_file$group <- paste0(GA1_cor_grid_4_file$snake_mu_rate, "_", GA1_cor_grid_4_file$snake_mu_effect_sd,"_",GA1_cor_grid_4_file$newt_mu_rate, "_", GA1_cor_grid_4_file$newt_mu_effect_sd)
GA1_cor_grid_4_file$sim=LETTERS[factor(GA1_cor_grid_4_file$group)]
GA1_cor_grid_4_file$grid_num = 4

GA1_cor_grid_5_file<- read.csv("~/Desktop/GA1_dif_grids/all_cor_5.txt" , header = TRUE)
GA1_cor_grid_5_file$group_rep <- paste0(GA1_cor_grid_5_file$snake_mu_rate, "_", GA1_cor_grid_5_file$snake_mu_effect_sd,"_",GA1_cor_grid_5_file$newt_mu_rate, "_", GA1_cor_grid_5_file$newt_mu_effect_sd, "_", GA1_cor_grid_5_file$rep)
GA1_cor_grid_5_file$group <- paste0(GA1_cor_grid_5_file$snake_mu_rate, "_", GA1_cor_grid_5_file$snake_mu_effect_sd,"_",GA1_cor_grid_5_file$newt_mu_rate, "_", GA1_cor_grid_5_file$newt_mu_effect_sd)
GA1_cor_grid_5_file$sim=LETTERS[factor(GA1_cor_grid_5_file$group)]
GA1_cor_grid_5_file$grid_num = 5

GA1_cor_grid_6_file<- read.csv("~/Desktop/GA1_dif_grids/all_cor_6.txt" , header = TRUE)
GA1_cor_grid_6_file$group_rep <- paste0(GA1_cor_grid_6_file$snake_mu_rate, "_", GA1_cor_grid_6_file$snake_mu_effect_sd,"_",GA1_cor_grid_6_file$newt_mu_rate, "_", GA1_cor_grid_6_file$newt_mu_effect_sd, "_", GA1_cor_grid_6_file$rep)
GA1_cor_grid_6_file$group <- paste0(GA1_cor_grid_6_file$snake_mu_rate, "_", GA1_cor_grid_6_file$snake_mu_effect_sd,"_",GA1_cor_grid_6_file$newt_mu_rate, "_", GA1_cor_grid_6_file$newt_mu_effect_sd)
GA1_cor_grid_6_file$sim=LETTERS[factor(GA1_cor_grid_6_file$group)]
GA1_cor_grid_6_file$grid_num = 6

GA1_cor_grid_7_file<- read.csv("~/Desktop/GA1_dif_grids/all_cor_7.txt" , header = TRUE)
GA1_cor_grid_7_file$group_rep <- paste0(GA1_cor_grid_7_file$snake_mu_rate, "_", GA1_cor_grid_7_file$snake_mu_effect_sd,"_",GA1_cor_grid_7_file$newt_mu_rate, "_", GA1_cor_grid_7_file$newt_mu_effect_sd, "_", GA1_cor_grid_7_file$rep)
GA1_cor_grid_7_file$group <- paste0(GA1_cor_grid_7_file$snake_mu_rate, "_", GA1_cor_grid_7_file$snake_mu_effect_sd,"_",GA1_cor_grid_7_file$newt_mu_rate, "_", GA1_cor_grid_7_file$newt_mu_effect_sd)
GA1_cor_grid_7_file$sim=LETTERS[factor(GA1_cor_grid_7_file$group)]
GA1_cor_grid_7_file$grid_num = 7

# GA1_grid_grid_2_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_2.txt" , header = TRUE)
# GA1_grid_grid_2_file$group_rep <- paste0(GA1_grid_grid_2_file$snake_mu_rate, "_", GA1_grid_grid_2_file$snake_mu_effect_sd,"_",GA1_grid_grid_2_file$newt_mu_rate, "_", GA1_grid_grid_2_file$newt_mu_effect_sd, "_", GA1_grid_grid_2_file$rep)
# GA1_grid_grid_2_file$group <- paste0(GA1_grid_grid_2_file$snake_mu_rate, "_", GA1_grid_grid_2_file$snake_mu_effect_sd,"_",GA1_grid_grid_2_file$newt_mu_rate, "_", GA1_grid_grid_2_file$newt_mu_effect_sd)
# GA1_grid_grid_2_file$sim=LETTERS[factor(GA1_grid_grid_2_file$group)]
# GA1_grid_grid_2_file$grid_num = 2
# 
# 
# GA1_grid_grid_3_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_3.txt" , header = TRUE)
# GA1_grid_grid_3_file$group_rep <- paste0(GA1_grid_grid_3_file$snake_mu_rate, "_", GA1_grid_grid_3_file$snake_mu_effect_sd,"_",GA1_grid_grid_3_file$newt_mu_rate, "_", GA1_grid_grid_3_file$newt_mu_effect_sd, "_", GA1_grid_grid_3_file$rep)
# GA1_grid_grid_3_file$group <- paste0(GA1_grid_grid_3_file$snake_mu_rate, "_", GA1_grid_grid_3_file$snake_mu_effect_sd,"_",GA1_grid_grid_3_file$newt_mu_rate, "_", GA1_grid_grid_3_file$newt_mu_effect_sd)
# GA1_grid_grid_3_file$sim=LETTERS[factor(GA1_grid_grid_3_file$group)]
# GA1_grid_grid_3_file$grid_num = 3
# 
# GA1_grid_grid_4_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_4.txt" , header = TRUE)
# GA1_grid_grid_4_file$group_rep <- paste0(GA1_grid_grid_4_file$snake_mu_rate, "_", GA1_grid_grid_4_file$snake_mu_effect_sd,"_",GA1_grid_grid_4_file$newt_mu_rate, "_", GA1_grid_grid_4_file$newt_mu_effect_sd, "_", GA1_grid_grid_4_file$rep)
# GA1_grid_grid_4_file$group <- paste0(GA1_grid_grid_4_file$snake_mu_rate, "_", GA1_grid_grid_4_file$snake_mu_effect_sd,"_",GA1_grid_grid_4_file$newt_mu_rate, "_", GA1_grid_grid_4_file$newt_mu_effect_sd)
# GA1_grid_grid_4_file$sim=LETTERS[factor(GA1_grid_grid_4_file$group)]
# GA1_grid_grid_4_file$grid_num = 4
# 
# GA1_grid_grid_5_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_5.txt" , header = TRUE)
# GA1_grid_grid_5_file$group_rep <- paste0(GA1_grid_grid_5_file$snake_mu_rate, "_", GA1_grid_grid_5_file$snake_mu_effect_sd,"_",GA1_grid_grid_5_file$newt_mu_rate, "_", GA1_grid_grid_5_file$newt_mu_effect_sd, "_", GA1_grid_grid_5_file$rep)
# GA1_grid_grid_5_file$group <- paste0(GA1_grid_grid_5_file$snake_mu_rate, "_", GA1_grid_grid_5_file$snake_mu_effect_sd,"_",GA1_grid_grid_5_file$newt_mu_rate, "_", GA1_grid_grid_5_file$newt_mu_effect_sd)
# GA1_grid_grid_5_file$sim=LETTERS[factor(GA1_grid_grid_5_file$group)]
# GA1_grid_grid_5_file$grid_num = 5
# 
# GA1_grid_grid_6_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_6.txt" , header = TRUE)
# GA1_grid_grid_6_file$group_rep <- paste0(GA1_grid_grid_6_file$snake_mu_rate, "_", GA1_grid_grid_6_file$snake_mu_effect_sd,"_",GA1_grid_grid_6_file$newt_mu_rate, "_", GA1_grid_grid_6_file$newt_mu_effect_sd, "_", GA1_grid_grid_6_file$rep)
# GA1_grid_grid_6_file$group <- paste0(GA1_grid_grid_6_file$snake_mu_rate, "_", GA1_grid_grid_6_file$snake_mu_effect_sd,"_",GA1_grid_grid_6_file$newt_mu_rate, "_", GA1_grid_grid_6_file$newt_mu_effect_sd)
# GA1_grid_grid_6_file$sim=LETTERS[factor(GA1_grid_grid_6_file$group)]
# GA1_grid_grid_6_file$grid_num = 6
# 
# GA1_grid_grid_7_file<- read.csv("~/Desktop/GA1_dif_grids/all_grid_7.txt" , header = TRUE)
# GA1_grid_grid_7_file$group_rep <- paste0(GA1_grid_grid_7_file$snake_mu_rate, "_", GA1_grid_grid_7_file$snake_mu_effect_sd,"_",GA1_grid_grid_7_file$newt_mu_rate, "_", GA1_grid_grid_7_file$newt_mu_effect_sd, "_", GA1_grid_grid_7_file$rep)
# GA1_grid_grid_7_file$group <- paste0(GA1_grid_grid_7_file$snake_mu_rate, "_", GA1_grid_grid_7_file$snake_mu_effect_sd,"_",GA1_grid_grid_7_file$newt_mu_rate, "_", GA1_grid_grid_7_file$newt_mu_effect_sd)
# GA1_grid_grid_7_file$sim=LETTERS[factor(GA1_grid_grid_7_file$group)]
# GA1_grid_grid_7_file$grid_num = 7

@@

@@

```{r, cor box set up}

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

boxplot_cor_grid_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(grid_num), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = factor(grid_num)))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  #unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

  return(plot)
}

hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  #stat_bin(bins=30)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

suppressMessages(print(plot))

  return(plot)
}

var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  real_snewt_var = var(snewt$dif)
  var_cor_table=data.frame()

  for(i in 1:length(unique(file$snake_newt_rep))){
    pattern<-unique(file$snake_newt_rep)[i]
    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]

    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
  }

  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)

  plot <- ggplot(var_cor_table) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

  return(plot)
}
